Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
only three more lines to kill

For each domain,
we are interested both in how many tasks the
agent can solve and how quickly it can find those solutions.
For symbolic regression, we also care about the quality
of the solution, as measured by the likelihood model $\probability[x|p]$,
which measures how many
real numbers were used in the program: e.g. did the model correctly explain a linear function
using two numbers, or did it introduce extraneous parameters?
Tbl.~\ref{baselineComparisons}
compares our model against these baselines.
Our full model consistently
beats the baselines,
and that the recognition model 
consistently increases the number of solved held-out tasks.
Lesioning the recognition model also slows down the convergence of the algorithm,
taking more wake/sleep cycles to reach a given number of tasks solved (Fig.~\ref{learningCurves}).
This supports our view of the recognition model as a way of accelerating the search over programs.

@@

 \noindent \emph{Neural recognition models for program induction:} Much recent work in the ML community has
 focused on creating neural networks that regress from
 input/output examples to programs~\cite{devlin2017robustfill,devlin2017neural,menon2013machine,balog2016deepcoder}. This family of work is closest to the lesioned version of
 \system where $(\mathcal{D},\theta)$ is held fixed and $q$ is learned (RF/DC baseline).
 These neural networks are typically trained with strong supervision (i.e., with annotated ground-truth programs) on massive data sets (i.e., hundreds of millions~\cite{devlin2017robustfill}).
 In our work we consider a weakly-supervised setting where ground truth programs are not provided and
 the agent must learn from a few hundred examples.

 \noindent \emph{Predicate Invention in ILP:} The Inductive Logic Programming (ILP) community
 has long worked on the problem of inventing new primitive predicates~\cite{DBLP:conf/ecai/LinDETM14,muggleton2015meta}, which is analogous to our model with $\theta$ held fixed and $q$ ablated.

 \noindent \emph{Inventing new subroutines for program induction:}
 Several program induction algorithms, most prominently the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}, take as their goal to learn new, reusable subroutines that are shared in a multitask setting. We find this work inspiring and motivating,
 and extend it along two dimensions: (1) we propose a new algorithm for
 inducing reusable subroutines, based on Fragment Grammars~\cite{tim} and Tree-Substitution Grammars~\cite{cohn2010inducing};
 and (2) we show how to combine these techniques with bottom-up neural recognition models.
 Other instances of this related idea are~\cite{DBLP:conf/icml/LiangJK10} and Schmidhuber's OOPS model~\cite{schmidhuber2004optimal}.

>>>>

For each domain,
we are interested both in how many tasks the
agent can solve and how quickly it can find those solutions.
For symbolic regression, we also care about the quality
of the solution, as measured by the likelihood model $\probability[x|p]$,
e.g. did the agent correctly explain a linear function
using two numbers, or did it introduce extraneous parameters?
Tbl.~\ref{baselineComparisons}
compares our model against these baselines.
Our full model consistently
beats the baselines,
and that the recognition model 
consistently increases the number of solved held-out tasks.
Lesioning the recognition model also slows down the convergence of the algorithm,
taking more wake/sleep cycles to reach a given number of tasks solved (Fig.~\ref{learningCurves}).
This supports our view of the recognition model as a way of accelerating the search over programs.

@@

 \noindent \emph{Neural recognition models for program induction:} Much recent work in the ML community has
 focused on creating neural networks that regress from
 input/output examples to programs~\cite{devlin2017robustfill,devlin2017neural,menon2013machine,balog2016deepcoder}. This family of work is closest to the lesioned version of
 \system where $(\mathcal{D},\theta)$ is held fixed and $q$ is learned (RF/DC baseline).
 These neural networks are typically trained with strong supervision (i.e., with annotated ground-truth programs) on massive data sets (i.e., hundreds of millions~\cite{devlin2017robustfill}).
 In our work we consider a weakly-supervised setting where ground truth programs are not provided and
 the agent must learn from a few hundred tasks.

 \noindent \emph{Inventing new subroutines for program induction:}
 Several program induction algorithms, most prominently the EC algorithm~\cite{Dechter:2013:BLV:2540128.2540316}, take as their goal to learn new, reusable subroutines that are shared in a multitask setting. We find this work inspiring and motivating,
 and extend it along two dimensions: (1) we propose a new algorithm for
 inducing reusable subroutines, based on Fragment Grammars~\cite{tim} and Tree-Substitution Grammars~\cite{cohn2010inducing};
 and (2) we show how to combine these techniques with bottom-up neural recognition models.
 Other instances of this related idea are~\cite{DBLP:conf/icml/LiangJK10} Schmidhuber's OOPS model~\cite{schmidhuber2004optimal}, and predicate invention in ILP~\cite{DBLP:conf/ecai/LinDETM14,muggleton2015meta}.
